---
title: "Lab 07 - Modelling course evaluations"
author: "Matthew Hurrell"
date: "`r Sys.Date()`"
output: html_document
---

### Packages and Data

```{r load-packages, message=FALSE, echo=TRUE}
library(tidyverse)
library(tidymodels)

```


```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


# Exercise 1: Exploratory Data Analysis

1.  Visualize the distribution of `score` in the dataframe `evals`.

```{r viz-score}
ggplot(data = evals)+
  geom_histogram(aes(x = score))

summary_evals <- evals %>% 
  summarise(mean(score), median(score))%>% 
  print()
```
There is a skew as more students rate the course highly compared to lowly. This was expected to see as the mean and median scores are over 4


2.  Visualize and describe the relationship between `score` and `bty_avg` using `geom_point()` to represent the data. 

```{r scatterplot}
ggplot(data = evals, aes(x = score, y = bty_avg))+
  geom_point()

ggplot(data = evals, aes(x = score, y = bty_avg))+
  geom_jitter()
```

Jittering is to randomly move points about around where they originally were. The original scatter point was misleading as many points were in the same spot leading to the density of points at a spot isnt communicated leading to the interpretation of the amount of dots and distribution of data to become misleading

# Exercise 2: Simple Linear regression with a numerical predictor

1. Fit a linear model called `score_bty_fit` to predict average professor evaluation `score` from average beauty rating (`bty_avg`). Print the regression output using `tidy()`.

```{r fit-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(bty_avg ~ score, data = evals)
```

```{r tidy-score_bty_fit}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(score_bty_fit)
```

score = 0.5255675*bty_avg+2.2237421

2. Plot the data again using `geom_jitter()`, and add the regression line.

```{r viz-score_bty_fit}
ggplot(data = evals, aes(x = bty_avg, y = score))+
  geom_jitter()+
  geom_smooth(method = "lm", se = FALSE)
```

3. Interpret the slope of the linear model in context of the data.

The linear model shows that as the bty_avg increases, the score increase too at a very slow increase

4. Interpret the intercept of the linear model in context of the data. Comment on whether or not the intercept makes sense in this context.

The intercept makes sense in this linear model as someone can have a beauty score of 0 and have a higher score overall.

5. Determine the $R^2$ of the model and interpret it in the context of the data.

```{r R2}

glance(score_bty_fit)$r.squared
```



6. Make a plot of residuals vs. predicted values for the model above.

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(___) + ...
```

# Exercise 3: Simple Linear regression with a categorical predictor

0. Look at the variable rank, and determine the frequency of each category level.

```{r}
# ... 
```

1. Fit a new linear model called `score_rank_fit` to predict average professor evaluation `score` based on `rank` of the professor.

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

2. Fit a new linear model called `score_gender_fit` to predict average professor evaluation `score` based on `gender` of the professor. 

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, eval=FALSE}
# remove eval = FALSE from the code chunk options
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
```

*Add your narrative here. Use in-line code!*

# Exercise 4: Multiple linear regression

1. Fit a multiple linear regression model, predicting average professor evaluation `score` based on average beauty rating (`bty_avg`) and `gender.`

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

```{r eval = FALSE}
ggplot(___) + ...
```

2. What percent of the variability in `score` is explained by the model `score_bty_gender_fit`. 

```{r}
# ...
```


3. What is the equation of the line corresponding to just male professors?

*Add your equation here.*

4. For two professors who received the same beauty rating, which gender tends to have the higher course evaluation score?

*Add your narrative here.*

5. How does the relationship between beauty and evaluation score vary between male and female professors?

*Add your narrative here.*

6. How do the adjusted $R^2$ values of `score_bty_fit` and `score_bty_gender_fit` compare? 

```{r eval=FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)$adj.r.squared
glance(___)$adj.r.squared
```

*Add your narrative here.*

7. Compare the slopes of `bty_avg` under the two models (`score_bty_fit` and `score_bty_gender_fit`).

*Add your narrative here.*

# Exercise 5: Interpretation of log-transformed response variables

If you do not know how to use LaTeX, do this exercise with pen and paper.
